Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-26 paper/paper.tex
Add to results.
Analyze results of TrueSimPref experiments.

Next, we consider the results of using $UserPredSim$ to estimate $TrueSimPref$.

@@

>>>>

@@

Next, we consider the results of using $UserPredSim$ to estimate $TrueSimPref$.
Recall that $UserSimPref$ corresponds to $CosSim$ as time goes to infinity. As
such, the relationship in our model between the covariance of the conditional
probability distributions that generate ratings given a similarity does not hold
for $TrueSimPref$. That is, in our model
\begin{align}
\mathbf{\Sigma_z} \neq \sigma_r^2 \cdot
\left[ \begin{array}{cc}  1 & z \\ z & 1 \end{array} \right],
\end{align}
where $\mathbf{\Sigma_z}$ is the covariance matrix of $P(\vec{R} | Z=z)$ with
$Z$ a random variable representing the $TrueSimPref$ of two items. Nonetheless,
we can choose parameters and naively use $UserPredSim$ to estimate
$TrueSimPref$. For this experiment, we choose $\mu_s = 0.054$, $\sigma_s =
0.049$, $\mu_r = 0.25$, $\sigma_r = 0.15$, and $\lambda = 0.002$ using the same
methods as before.

In Fig. \ref{fig:MSE_SimP} we show the results of our experiments estimating
$TrueSimPref$ using the $N \geq 80$ data set. The MSE of $CosSim$, like that of
$PearSim$ in the case of $TrueSimRand$, rapidly diverges as the number of common
users $n$ goes to zero. Interestingly, $CosSim$ outperforms
always-guess-the-average for all $n > 25$, in contrast with $PearSim$, which
does the same only after $n > 45$. The speaks to the greater stability of
$CosSim$, which takes into consideration all ratings, not only those from common
users. Meanwhile, the $LinRegSim$ performs surprisingly similar for estimations
of $TrueSimPref$ and $TrueSimRand$. In both cases, the MSE begins at
approximately that of always-guess-the-average for $n = 1$ and then decreases
approximately linearly with increasing $n$. Indeed, this was also true for the
$N \geq 40$ experiment. We attribute this robustness to the fact that the model
from which $LinRegSim$ is derived abstracts away the underlying mechanism from
which $TrueSim$ is computed. Finally, $UserPredSim$, perhaps surprisingly, has
the lowest MSE for $n < 15$, although not by much. For all $n > 15$, $LinRegSim$
outperforms $UserPredSim$ in estimating $TrueSimPref$. And for all $n > 40$,
$CosSim$ achieves lower MSE than that of $UserPredSim$. This lackluster
performance by $UserPredSim$ might be expected, however, given the model on
which it is based is a dubious fit for $TrueSimPref$.
